### 2018-05-29 manuscript/data.tex
data

\section{Data}

The advent of mobile sensing techniques makes it possible to develop urban geography from social media source. Complement the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time, which reaches a wide range of individuals as well as collects the movement in human inactive time, such as the mid-night.

In this work, we performed the demographical survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(b)). Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(c)). Each trip requires the information of start/end location and time, the traveling purpose and modes. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(d)).

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/survey_app}
 \caption{Collecting Interface: (a) welcome page; (b) personal characteristics collecting page; (c) trips collecting page; (d) credit system page}
 \label{fig:app}
\end{figure}

Over the releasing time period from June to October in 2015, 25481 individules (48\% females and 52\% males) were reached and XXX trips are collected. The majority of our 25481 volunteers contribute XXX trips. Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains. Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_over}
 \caption{Profile of Individual: XX variables falling into 8 domains enriches the analysis of urban dynamics}
 \label{fig:data_over}
\end{figure}

In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban. Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution aligns to the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.

>>>>

\section{Online Census}

The advent of mobile sensing techniques makes it possible to develop urban geography from social media source. Complementary to the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time. It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics from social, economic and deomgraphic aspects. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)). Besides to those static features, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)). Each trip requires the information of start/end location and time, the traveling purpose and modes. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards those with the top credits (Figure~\ref{fig:app}(c)).

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/survey_app}
 \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page}
 \label{fig:app}
\end{figure}

Figure~\ref{fig:data_over} lists the 8 domains, which give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_over}
 \caption{Profile of Individual: 8 domains about individual characteristics enrich the analysis of mobility patterns}
 \label{fig:data_over}
\end{figure}

\subsection{Basic Statistics of Data}

Over the releasing time period from \m{June to October} in 2015, 25481 individules (48\% females and 52\% males) were reached and \m{XXX} trips are collected. The majority of our 25481 volunteers contribute \m{XXX} trips.

@@

In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban. Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution aligns to the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.

### 2018-05-29 manuscript/relatedwork.tex
intro...
data

The related work is expanded around the visual analytics of spatial patterns in the context of urban. In the past decades, the power of visual analytics in exploring spatial-temporal data has been regcognized and well developped. Andrienko et al.~\cite{andrienko2013visual} summarise the spatio-temporal data to spatial, temporal and thematic components. Most of them focus on the analysis of anonymous movement patterns. The presense of social media makes it possible to embed the spatial analysis with semnatic explanation, but most of them emphasizing thematic information of moving. In this work, we aim to continue to narrow the gap between mobility patterns and individuals' charecteristic features.

\textbf{Anonymous Movement Analysis}

 With the development of location-acquistion techniques, massive spatial trajectories are generated, which represent the mobility of various moving objects. Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} et al. construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behaviour based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behaviour among multiple routes.

@@

Different from anonymous movement analysis, in this work, we focus on investigating the how the mobility patterns varies to individual characteristics. We perform a census experiment via Social Media to collect the real information from volunteers, to get rid of indirect data inferring.

>>>>

This work concerns to the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presense of geo-tagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data, but focus more on individual charecteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related work do.

\textbf{Movement Data Analysis}

 With the development of location-acquistion techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} et al. construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behaviour based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behaviour among multiple routes.

@@
